---
title: "QP Data Analysis"
author: "Diana Sanchez"
date: "August 2022"
output: html_document
---


rm(list = ls(all.names = TRUE)) #clear R environment


# Load libraries
```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(GGally)
library(speakr)
library(dplyr)
library(tidyverse)
library(readr)
library(plyr)
library(stringi)
library(purrr)
library(broom)
library(scatterplot3d)
library(kableExtra)

library(tidyr)
library(readr)
library(readxl)

# get summary table for lm results
library(gtsummary)
library(finalfit) # works with plyr
library(jtools)
library(texreg)
library(kableExtra)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(stargazer)
```


# Loading raw data for experiment tasks 
Loading .txt data anc converting .cvs to df

## Loading raw data for backward
```{r}
setwd("~/Desktop/RStudio_QP/experiment_rawdata")

#Load backward raw data
all_backward <- file.path("~/Desktop/RStudio_QP/experiment_rawdata/Backward") 
#Create list files
backward_file_names <- list.files(all_backward, pattern = ".txt", full.names = TRUE) 
#turns list to list object (output)
backward_data <- lapply(backward_file_names, read.table)
#change file names
names(backward_data) <- stri_sub(backward_file_names, -9, -5)

#backward_data    #use this to read df

#data frame
backward_df <- do.call("rbind", backward_data)
#converts values to string
str(backward_df)

backward_df <- tibble::rownames_to_column(backward_df, "row_name")
colnames(backward_df) <- c("participant_observationNum","highest_corsi","Number_of_items","backward_result","table_row")

#saving df
write.csv(backward_df,"~/Desktop/RStudio_QP/experiment_rawdata/all_backward.csv")
```

## Loading raw data for flanker
```{r}
setwd("~/Desktop/RStudio_QP/experiment_rawdata")

#Load backward raw data
all_flanker <- file.path("~/Desktop/RStudio_QP/experiment_rawdata/Flanker") 
#Create list files
flanker_file_names <- list.files(all_flanker, pattern = ".txt", full.names = TRUE) 
#turns list to list object (output)
flanker_data <- lapply(flanker_file_names, read.table)

#change file names
names(flanker_data) <- stri_sub(flanker_file_names, -9, -5)


#flanker_data       #use this only to read df

#data frame
flanker_df <- do.call("rbind", flanker_data)

str(flanker_df)

flanker_df <- tibble::rownames_to_column(flanker_df, "row_name")
colnames(flanker_df) <- c("participant_observationNum","stimulus", "congruent","flanker_result","response_time")

#saving df
write.csv(flanker_df,"~/Desktop/RStudio_QP/experiment_rawdata/all_flanker.csv")
```

## Loading raw data for stroop
```{r}
setwd("~/Desktop/RStudio_QP/experiment_rawdata")

#Load backward raw data
all_stroop <- file.path("~/Desktop/RStudio_QP/experiment_rawdata/Stroop") 
#Create list files
stroop_file_names <- list.files(all_stroop, pattern = ".txt", full.names = TRUE) 
#turns list to list object (output)
stroop_data <- lapply(stroop_file_names, read.table)

#change file names
names(stroop_data) <- stri_sub(stroop_file_names, -9, -5)

#stroop_data        #use this only to read df

#data frame
stroop_df <- do.call("rbind", stroop_data)

str(stroop_df)

stroop_df <- tibble::rownames_to_column(stroop_df, "row_name")
colnames(stroop_df) <- c("participant_observationNum","stimulus", "word_name","word_color","stroop_match", "row_number","key_pressed", "stroop_result", "response_time")

#saving df
write.csv(stroop_df,"~/Desktop/RStudio_QP/experiment_rawdata/all_stroop.csv")
```




#Analysis of all_data 
## Tidy all_data
all_data df includes all 58 participants, two groups. Only total correct responses are included for each experimental task (flanker, stroop, backward).
```{r}
#Load working data
all_data <- read.csv("~/Desktop/RStudio_QP/experiment_data/all_data.csv", header = TRUE) 

#summary
summary(all_data)


#adding "bilingual"column to data set (all_data)
all_data$bilingual = c(rep(0,36),rep(1,22)) # 0=nonLanguage, 1=language


#separate groups: nonLanguage teachers and language teachers
nonLanguage <- all_data[1:36, ]
language <- all_data[37:58, ]

nonLanguage$language = "NonLanguage"
language$language = "Language"

#adding column to indicate nonLanguage or language for each participant
all_data = bind_rows(nonLanguage,language)
```



##Analysis of each experiment + group+age+IQ
```{r}
stroop_data = lm(stroop_correct ~ bilingual+age+IQ, data=all_data)
summary(stroop_data)
```

```{r}
flanker_data = lm(flanker_correct ~ bilingual+age+IQ, data=all_data)
summary(flanker_data)
```

```{r}
backward_data = lm(backward_correct ~ bilingual+age+IQ, data=all_data)
summary(backward_data)
```


# Analsyis by groups
Data Analysis for nonLanguage Group
The nonLanguage group consist of the teachers who only use one language in their professional work setting.

## Linear regression model for nonLanguage BACKWARD task
```{r}
data(nonLanguage)
head(nonLanguage)

##plot
plot(backward_correct ~ age + IQ, data = nonLanguage, pch=16)

#linear model
backward_model_nonLanguage <- lm(backward_correct ~ age + IQ, data = nonLanguage)
#abline(backward_model_nonLanguage)

my_results <- tidy(backward_model_nonLanguage)
my_results
backward_model_nonLanguage

summary(backward_model_nonLanguage)

par(mfrow = c(2,2)) 
plot(backward_model_nonLanguage) 

AIC(backward_model_nonLanguage)
BIC(backward_model_nonLanguage)

###
test2 = lm(backward_correct ~ bilingual+age+IQ, data=all_data)
summary(test2)

```

## Linear regression model for nonLanguage FLANKER task
```{r}
data(nonLanguage)
head(nonLanguage)

##plot
plot(flanker_correct ~ age + IQ, data = nonLanguage, pch=16)

#linear model
flanker_model_nonLanguage <- lm(flanker_correct ~ age + IQ, data = nonLanguage)
#abline(flanker_model_nonLanguage)

my_results <- tidy(flanker_model_nonLanguage)
my_results
flanker_model_nonLanguage


summary(flanker_model_nonLanguage)

par(mfrow = c(2,2)) 
plot(flanker_model_nonLanguage) 

AIC(flanker_model_nonLanguage)
BIC(flanker_model_nonLanguage)

#comparing language and nonLanguage groups for flanker_correct
test = lm(flanker_correct ~ bilingual+age+IQ, data=all_data)
summary(test)

```

## Linear regression model for nonLanguage STROOP task
```{r}
data(nonLanguage)
head(nonLanguage)

##plot
plot(stroop_correct ~ age + IQ, data = nonLanguage, pch=16)

#linear model
stroop_model_nonLanguage <- lm(stroop_correct ~ age + IQ, data = nonLanguage)
abline(stroop_model_nonLanguage)

my_results <- tidy(stroop_model_nonLanguage)
my_results
stroop_model_nonLanguage

summary(stroop_model_nonLanguage)

par(mfrow = c(2,2)) 
plot(stroop_model_nonLanguage) 

AIC(stroop_model_nonLanguage)
BIC(stroop_model_nonLanguage)


test3 = lm(stroop_correct ~ bilingual+age+IQ, data=all_data)
summary(test3)
```


# Data Analysis for Language Group {.tabset}
The language group consist of the teachers who use more than one language in their professional work setting.

## Linear regression model for language BACKWARD
```{r}
data(language)
head(language)

#plot Language
plot(backward_correct ~ age + IQ, data = language, pch=16)

#linear model
backward_model_language <- lm(backward_correct ~ age + IQ, data = language)
abline(backward_model_language)

my_results <- tidy(backward_model_language)
my_results
backward_model_language

summary(backward_model_language)

par(mfrow = c(2,2)) 
plot(backward_model_language) 

AIC(backward_model_language)
BIC(backward_model_language)
```

## Linear regression model for language FLANKER
```{r}
data(language)
head(language)

#plot Language
plot(flanker_correct ~ age + IQ, data = language, pch=16)

#linear model
flanker_model_language <- lm(flanker_correct ~ age + IQ, data = language)
abline(flanker_model_language)

my_results <- tidy(flanker_model_language)
my_results
flanker_model_language

summary(flanker_model_language)

par(mfrow = c(2,2)) 
plot(flanker_model_language) 

AIC(flanker_model_language)
BIC(flanker_model_language)
```

## Linear regression model for language STROOP
```{r}
data(language)
head(language)

#plot Language
par(mfrow = c(2,2))
plot(stroop_correct ~ age + IQ, data = language, pch=16)

#linear model
stroop_model_language <- lm(stroop_correct ~ age + IQ, data = language)

par(mfrow = c(2,2))
plot(stroop_model_language)

my_results <- tidy(stroop_model_language)
my_results
stroop_model_language

summary(stroop_model_language)

par(mfrow = c(2,2)) 
plot(stroop_model_language) 

AIC(stroop_model_language)
BIC(stroop_model_language)
```


#ADDITIONAL ANALYSIS

## Histogram to observe results
```{r}
attach(all_data) #using objects in df all_data
hist(backward_correct) #this could be considered "normal"
hist(flanker_correct) #not normal
hist(stroop_correct) #not normal

summary(all_data)
```




#-------------------------------------------------------------------------#

## Removing 1 data (45) which is considered an outlier. 

```{r}
#created new data with deleted row 45
new_all_data <- all_data[-c(45),]

#created new language group (-45)
new_language <- new_all_data[37:58, ]

summary(new_all_data)
```

# Linear regression for Stroop
```{r}
#Data analysis of 3 tasks and groups with "new_all_data" df
stroop_data = lm(stroop_correct ~ bilingual+age+IQ, data=new_all_data)
summary(stroop_data)

#table for summary results
tbl_regression(stroop_data, exponentiate = FALSE) #created table
summ(stroop_data, scale = FALSE) #another table
broom::tidy(stroop_data) #table for summary

#Table for Stroop lm results
tab_model(stroop_data,
          dv.labels = c("Stroop Task"),
          string.pred = "Coefficient",
          string.p ="P-Value")#printed table for summary


#plot IQ
ggplot(new_all_data, aes(x =IQ, y = stroop_correct, color = language)) +
  geom_point() +
   scale_fill_discrete(labels = c('Languages','One Language')) +
  guides(colour = guide_legend(title = "Teachers")) +
labs(title = "Stroop Task Performance", y= "Correct Trials", x= "Intelligence Quotient") +
  theme(plot.title=element_text(hjust=0.5))
 
#plot age
ggplot(new_all_data, aes(x =age, y = stroop_correct, color = language)) +
  geom_point() +
   scale_fill_discrete(labels = c('Languages','One Language')) +
  guides(colour = guide_legend(title = "Teachers")) +
labs(title = "Stroop Task Performance", y= "Correct Trials", x= "Age") +
  theme(plot.title=element_text(hjust=0.5))

##Assumptions of Linear Regression *Keys: 1, 2, 3, 4, 5. Ex. plot(stroop_data, 5)
par(mfrow = c(2,2))
plot(stroop_data)
```

```{r}

flanker_data = lm(flanker_correct ~ bilingual+age+IQ, data=new_all_data)
summary(flanker_data)

tbl_regression(flanker_data, exponentiate = FALSE,) #created table
summ(flanker_data, scale = FALSE) #another table
broom::tidy(flanker_data) #table for summary


#Table for Flanker lm results
tab_model(flanker_data,
          dv.labels = c("Flanker Task"),
          string.pred = "Coeffcient",
          string.ci = "Conf. Int",
          string.p ="P-Value")#printed table for summary

#plot IQ
ggplot(new_all_data, aes(x =IQ, y = flanker_correct, color = language)) +
  geom_point() +
   scale_fill_discrete(labels=c('Languages','One Language')) +
  guides(colour = guide_legend(title = "Teachers")) +
labs(title = "Flanker Task Performance", y= "Correct Trials", x= "Intelligence Quotient") +
  theme(plot.title=element_text(hjust=0.5))

#plot AGE
ggplot(new_all_data, aes(x = age, y = flanker_correct, color = language)) +
  geom_point() +
   scale_fill_discrete(labels = c('Languages','One Language')) +
  guides(colour = guide_legend(title = "Teachers")) +
labs(title = "Flanker Task Performance", y= "Correct Trials", x= "Age") +
  theme(plot.title=element_text(hjust=0.5))

par(mfrow = c(2,2))
plot(flanker_data)
```


```{r}

backward_data = lm(backward_correct ~ bilingual+age+IQ, data=new_all_data)
summary(backward_data)

tbl_regression(backward_data, exponentiate = FALSE) #created table
summ(backward_data, scale = FALSE) #another table

#Table for backward corsi lm results
tab_model(backward_data,
          dv.labels = c("Backward Corsi Task"),
          string.pred = "Coeffcient",
          string.p ="P-Value")#printed table for summary

ggplot(new_all_data, aes(x =IQ, y = backward_correct, color = language)) +
  geom_point() +
   scale_fill_discrete(labels = c('Languages','One Language')) +
  guides(colour = guide_legend(title = "Teachers")) +
labs(title = "Backward Corsi Task Performance", y= "Correct Trials", x= "Intelligence Quotient") +
  theme(plot.title=element_text(hjust=0.5))

#plot AGE
ggplot(new_all_data, aes(x =age, y = backward_correct, color = language)) +
  geom_point() +
   scale_fill_discrete(labels = c('Languages','One Language')) +
  guides(colour = guide_legend(title = "Teachers")) +
labs(title = "Backward Corsi Task Performance", y= "Correct Trials", x= "Age") +
  theme(plot.title=element_text(hjust=0.5))


par(mfrow = c(2,2))
plot(backward_data)
```

```{r}
## Print all 3 regression results

tab_model(flanker_data, backward_data, stroop_data,
          dv.labels = c("Flanker Task", "Backward Corsi Task", "Stroop Task"),
string.p ="P-Value")#printed table for summary

```

## Background Questionnaire
```{r}
background_survey <- read.csv("~/Desktop/RStudio_QP/experiment_data/background_survey.csv", header = TRUE)


#background_survey <- background_survey %>% select(-c(X,Please.enter.your.Prolific.ID...Participant.ID..or.full.name,X.1))

#background_survey %>%
  #kbl(caption = "Background data") %>%
 # kable_classic(full_width = F, html_font = "Cambria") 

#str(background_survey)


```


```{r }
str(background_survey)
background_survey$Age <- as.numeric(background_survey$Age)
background_survey_1  <- background_survey[1:57,] 
background_survey_1

library(table1)
table1(~Bilingual + Age + Ethnicity + Experience | Gender , data = background_survey_1) 

table1(~Bilingual + Age+Ethnicity | Gender , data = background_survey_1,topclass = "Rtable1-grid")


table1(~Bilingual + Residence + Teaching_Level + Experience | Gender , data = background_survey_1) 


```


```{r}
#plot Language
plot(flanker_correct ~ age + IQ, data = new_language, pch=16)

#linear model
flanker_model_language <- lm(flanker_correct ~ age + IQ, data = new_language)
abline(flanker_model_language)

my_results <- tidy(flanker_model_language)
my_results
flanker_model_language

summary(flanker_model_language)

par(mfrow = c(2,2)) 
plot(flanker_model_language) 

par(mfrow = c(2,2)) 
plot(flanker_model_language, 1)

##
#plot Language
par(mfrow = c(2,2))
plot(stroop_correct ~ age + IQ, data = new_language, pch=16)

#linear model
stroop_model_language <- lm(stroop_correct ~ age + IQ, data = new_language)

par(mfrow = c(2,2))
plot(stroop_model_language)

my_results <- tidy(stroop_model_language)
my_results
stroop_model_language

summary(stroop_model_language)

```













